|

### 2021-07-13 paper/supplement-vignette.Rmd
Update supplement-vignette.Rmd
Minor edits for flow.

Pedigrees define familial relationships in a hierarchical structure. Many genomics tools for working with pedigrees start with a "fam" file, which is a tabular format with one row per individual and columns for unique IDs of the mother, father, and the family unit.

One of the formats used by PLINK and other genetic analysis tools is the `.fam` file.[^plink-fam] The package includes `read_fam()` to read files in this format:

@@

Family structures in the "fam" format can then be translated to the `pedigree` structure used by the `kinship2` package.[^kinship2-vignette] The "fam" format could include multiple families, and the `fam2ped()` function will collapse them all into a `tibble` with one row per family:

@@

The `plot_pedigree()` function from `skater` will walk over a list of pedigree objects, writing a multi-page PDF, with each page containing a pedigree from each of the families:

>>>>

Pedigrees define familial relationships in a hierarchical structure.

One of the formats used by PLINK and other genetic analysis tools is the `.fam` file,[^plink-fam] which is a tabular format with one row per individual and columns for unique IDs of the mother, father, and the family unit. The package includes `read_fam()` to read files in this format:

@@

Family structures imported from "fam" formated files can then be translated to the `pedigree` structure used by the `kinship2` package.[^kinship2-vignette] The "fam" format may include multiple families, and the `fam2ped()` function will collapse them all into a `tibble` with one row per family:

@@

The `plot_pedigree()` function from `skater` will iterate over a list of pedigree objects, writing a multi-page PDF, with each page containing a pedigree from each family:
